25-Figure3-051821

### 2021-11-16 notebooks/02-Figure2-051321.Rmd
updated supp figure notebooks

# Load packages
```{r, message=FALSE,warning=FALSE}
if (!require('tidyverse')) {
   remotes::install_version("tidyverse", version = "1.3.0", repos = "http://cran.us.r-project.org")
   library(tidyverse)
}
if (!require('glue')) {
   remotes::install_version("glue", version = "1.4.1", repos = "http://cran.us.r-project.org")
   library(glue)
}
if (!require('cowplot')) {
   remotes::install_version("cowplot", version = "1.0.0", repos = "http://cran.us.r-project.org")
   library(cowplot)
}
if (!require('ggpubr')) {
   remotes::install_version('foreign',version="0.8-72", repos = "http://cran.us.r-project.org")
   remotes::install_version("ggpubr", version = "0.4.0", repos = "http://cran.us.r-project.org")
   library(ggpubr)
}
if (!require('ggsignif')) {
   remotes::install_version("ggsignif", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(ggsignif)
}
if (!require('RColorBrewer')) {
   remotes::install_version("RColorBrewer", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(RColorBrewer)
}

@@

# Load input dataframe
```{r}
#df_filename <-snakemake$input$df_filename
#random_df_filename <-snakemake$input$df_filename
pcc_df <- read_csv(snakemake@input[['pcc_df']])
pcc_df_random <- read_csv(snakemake@input[['pcc_df_random']])%>%mutate(random_id=factor(random_id))
pcc_df <- pcc_df %>%
  mutate(data = "pcc") %>%
  mutate(sens_norm = sens / nrow(.), eff_norm = eff / nrow(.), group = "real") %>%
  bind_rows(
    pcc_df_random %>% mutate(data = "pcc") %>% mutate(sens_norm = sens / nrow(pcc_df), eff_norm = eff / nrow(pcc_df), group = "random")
  ) %>%
  mutate(group = fct_relevel(group, c("real", "random")))

@@

# Figure2 A,B
```{r}
real_random_labels <- c("PSN", "Rewired\nnetwork")
names(real_random_labels) <- c("real", "random")
pcc_deg_eff <- pcc_df %>% filter(group == "real") %>% # pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
  ggplot(aes(x = deg, y = eff_norm)) +
  geom_point() +
  #    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
  theme_bw() +
  ylab("Effectiveness (a.u.)") +
  xlab("Degree") +
  stat_cor(method = "pearson", cor.coef.name = "R", label.x.npc = 0.1) +
  theme(strip.text.y = element_text(angle = 0)) +
  scale_y_continuous(labels = scales::label_scientific(digits = 1))
pcc_deg_sens <- pcc_df %>% filter(group == "real") %>% # pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
  ggplot(aes(x = deg, y = sens_norm)) +
  geom_point() +
  #    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
  theme_bw() +
  ylab("Sensitivity (a.u.)") +
  xlab("Degree") +
  stat_cor(method = "spearman", cor.coef.name = "rho", label.x.npc = 0.1) +
  theme(strip.text.y = element_text(angle = 0)) +
  scale_y_continuous(labels = scales::label_scientific(digits = 1))
deg_scatter_plots <- cowplot::plot_grid(pcc_deg_eff, pcc_deg_sens,
  labels = c("A", "B"),
  ncol = 2
)
deg_scatter_plots
#ggsave("reports/figures/paper_figures_0202_pcc_only/fig2.png", plot = deg_scatter_plots, width = 10, height = 10)
print(cor.test(pcc_df$deg[pcc_df$deg<10],pcc_df$sens[pcc_df$deg<10],method='spearman',exact=FALSE))
```

# Figure2 C,D,E
```{r}
pcc_rewire_df <- pcc_df_random%>%group_by(random_id)%>%
  summarise(
    eff_deg_pearson = cor.test(eff,deg)$estimate,
    sens_deg_spearman = cor.test(sens,deg, method="spearman")$estimate
  )
rewire_df <- pcc_rewire_df %>% mutate(data = "pcc")
network_labels <- c("Yeast GI Profile Similarity")
facet_labels <- network_labels
names(facet_labels) <- c("pcc")
combined_rewire_df <- rewire_df %>%
  select(data, eff_deg_pearson, sens_deg_spearman) %>%
  mutate(type = "random") %>%
  bind_rows(
    data.frame(
      sens_deg_spearman = c(cor(pcc_df[pcc_df$group == "real", ]$deg, pcc_df[pcc_df$group == "real", ]$sens, method = "spearman")),
      eff_deg_pearson = c(cor(pcc_df[pcc_df$group == "real", ]$deg, pcc_df[pcc_df$group == "real", ]$eff, method = "pearson")), type = "real", data = c("pcc")
    )
  ) %>%
  mutate(data = fct_relevel(data, c("pcc")))

p3 <-
  ggplot() +
  #    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
  #    geom_boxplot()+
  #    geom_jitter()+
  geom_density(data = combined_rewire_df %>% filter(type != "real"), aes(x = eff_deg_pearson, color = type, y = ..scaled..), linetype = "dashed") +
  geom_vline(data = combined_rewire_df %>% filter(type == "real"), aes(xintercept = eff_deg_pearson, color = type)) +
  guides(color = guide_legend(title = "Data type"), shape = guide_legend(title = "Network type")) +
  ylab("Density") +
  xlab("Effectiveness degree correlation") +
  theme_bw() +
  theme(panel.spacing = unit(2, "lines")) +
  scale_y_continuous(expand = c(0, 0))
p4 <-
  ggplot() +
  #    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
  #    geom_boxplot()+
  #    geom_jitter()+
  geom_density(data = combined_rewire_df %>% filter(type != "real"), aes(x = sens_deg_spearman, y = ..scaled.., color = type), linetype = "dashed") +
  geom_vline(data = combined_rewire_df %>% filter(type == "real"), aes(xintercept = sens_deg_spearman, color = type)) +
  guides(color = guide_legend(title = "Data type"), shape = guide_legend(title = "Network type")) +
  ylab("Density") +
  xlab("Sensitivity degree correlation") +
  theme_bw() +
  theme(panel.spacing = unit(2, "lines"), legend.position = "bottom") +
  scale_color_discrete(labels = c("Random networks", "Genetic network")) +
  scale_y_continuous(expand = c(0, 0))
lgn34 <- cowplot::get_legend(p4)

pcc_degree_dens <- cowplot::ggdraw(plot_density_prs(pcc_df, deg, xlab = "Degree") + theme(legend.position = "none")) #+
distr_plots <- plot_grid(pcc_degree_dens + theme(legend.position = ""),
  ggdraw(p3 + theme(legend.position = "")),
  ggdraw(p4 + theme(legend.position = "")),
  labels = c("C", "D", "E"), nrow = 1
)
# distr_plots_withlgn <- plot_grid(distr_plots, lgn34,
# nrow=2,rel_heights = c(0.9,0.1))
# ggsave('reports/figures/paper_figures_0916/fig2.png',plot=distr_plots , width=7)
distr_plots
#plot_grid(deg_scatter_plots, distr_plots, pcc_dens_comb, nrow = 3, rel_heights = c(0.3, 0.4, .3))
#
#ggsave("reports/figures/paper_figures_0202_pcc_only/fig3.pdf", width = 10, height = 12)
```

# Figure2 G, F
```{r}
pcc_eff_dens <-
  plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness")
dens_lgn <- cowplot::get_legend(pcc_eff_dens + theme(legend.position = "right"))
#  cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
pcc_eff_dens <-
  cowplot::ggdraw(plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness") + theme(legend.position = "none") +
    coord_trans(x = "log10", xlim = c(NA, 10e-2)) +
    scale_x_continuous(
      breaks = scales::trans_breaks("log10", function(x) 10^x),
      labels = scales::trans_format("log10", scales::math_format(10^.x))
    )) #+
#   cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
# annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
pcc_sensitivity_dens <-
  cowplot::ggdraw(plot_density_prs(pcc_df, sens_norm, xlab = "Sensitivity (a.u.)") + theme(legend.position = "none")) #+
#        cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
# title <- cowplot::ggdraw() + cowplot::draw_label("Yeast GI Profile Similarity", fontface='bold')
pcc_dens_comb <- cowplot::plot_grid(pcc_eff_dens + theme(legend.position = "none"),
  pcc_sensitivity_dens + theme(legend.position = "none"),
  #+theme(legend.position='none'),
  labels = c("F", "G"), ncol = 2
)
# pcc_dens_comb_title = cowplot::plot_grid(title, pcc_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
# dens_lgn = cowplot::get_legend(pcc_sensitivity_dens)
#dens_plots <- 
  pcc_dens_comb

@@

```{r}
if(snakemake@params['save']==TRUE){
  figure_folder = "reports/figures/paper_figures_052521/"
combined_plot <- plot_grid(deg_scatter_plots, distr_plots, pcc_dens_comb, nrow = 3, rel_heights = c(0.3, 0.2, .3))
ggsave(glue("{figure_folder}/fig2.png"),plot=combined_plot,width=10,height=12)
}
```

>>>>

# Load packages
```{r message=FALSE, warning=FALSE}
if (!require('tidyverse')) {
   remotes::install_version("tidyverse", version = "1.3.0", repos = "http://cran.us.r-project.org")
   library(tidyverse)
}
if (!require('glue')) {
   remotes::install_version("glue", version = "1.4.1", repos = "http://cran.us.r-project.org")
   library(glue)
}
if (!require('cowplot')) {
   remotes::install_version("cowplot", version = "1.0.0", repos = "http://cran.us.r-project.org")
   library(cowplot)
}
if (!require('ggpubr')) {
   remotes::install_version('foreign',version="0.8-72", repos = "http://cran.us.r-project.org")
   remotes::install_version("ggpubr", version = "0.4.0", repos = "http://cran.us.r-project.org")
   library(ggpubr)
}
if (!require('ggsignif')) {
   remotes::install_version("ggsignif", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(ggsignif)
}
if (!require('RColorBrewer')) {
   remotes::install_version("RColorBrewer", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(RColorBrewer)
}

@@

# Load input dataframe
```{r}
# smake<-setClass("smake",slots=list(input="list"))
# snakemake <- new("smake",input=list("sensor_connectivity_df"="../data/interim/sensor_connectivity_df.csv", "pcc_df"='../data/interim/pcc_df.csv',"sensors_pcc"="../data/interim/sensors_df.csv",'effector_pcc'='../data/interim/effectors_df.csv',
# "rwr_row"="../data/interim/rwr_ranked_goa_rows.csv","prs_row"="../data/interim/prs_ranked_goa_rows.csv",
# "rwr_column"="../data/interim/rwr_ranked_goa_columns.csv","prs_column"="../data/interim/prs_ranked_goa_columns.csv"))
```

```{r tags=c()}
#df_filename <-snakemake$input$df_filename
#random_df_filename <-snakemake$input$df_filename
pcc_df <- read_csv(snakemake@input[['pcc_df']])
pcc_df_random <- read_csv(snakemake@input[['pcc_df_random']])%>%mutate(random_id=factor(random_id))
pcc_df <- pcc_df %>%
  mutate(data = "pcc") %>%
  mutate(sens_norm = sens / nrow(.), eff_norm = eff / nrow(.), group = "real") %>%
  bind_rows(
    pcc_df_random %>% mutate(data = "pcc") %>% mutate(sens_norm = sens / nrow(pcc_df), eff_norm = eff / nrow(pcc_df), group = "random")
  ) %>%
  mutate(group = fct_relevel(group, c("real", "random")))

@@

```{r}
text_size = 15
label_size = 17
```

# Figure2 A,B
```{r}
real_random_labels <- c("PSN", "Rewired\nnetwork")
names(real_random_labels) <- c("real", "random")
pcc_deg_eff <- pcc_df %>% filter(group == "real") %>% # pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
  ggplot(aes(x = deg, y = eff_norm)) +
  geom_point() +
  #    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
  theme_bw() +
  ylab("Effectiveness (a.u.)") +
  xlab("Degree") +
  stat_cor(method = "pearson", cor.coef.name = "R", label.x.npc = 0.1,size=8) +
  theme(strip.text.y = element_text(angle = 0),axis.text=element_text(size=text_size),axis.title = element_text(size=label_size)) +
  scale_y_continuous(labels = scales::label_scientific(digits = 1))
pcc_deg_sens <- pcc_df %>% filter(group == "real") %>% # pivot_longer(cols=sens_norm:eff_norm, names_to="prs_data_type", values_to="prs_data_value")%>%
  ggplot(aes(x = deg, y = sens_norm)) +
  geom_point() +
  #    facet_grid(rows = vars(group), scales='free', labeller =labeller(group= real_random_labels ) ) +
  theme_bw() +
  ylab("Sensitivity (a.u.)") +
  xlab("Degree") +
  stat_cor(method = "spearman", cor.coef.name = "rho", label.x.npc = 0.1, size=8) +
  theme(strip.text.y = element_text(angle = 0),axis.text=element_text(size=text_size),axis.title = element_text(size=label_size)) +
  scale_y_continuous(labels = scales::label_scientific(digits = 1))
deg_scatter_plots <- cowplot::plot_grid(pcc_deg_eff, pcc_deg_sens,
  labels = c("A", "B"),
  ncol = 2,label_size = 20
)
deg_scatter_plots
#ggsave("reports/figures/paper_figures_0202_pcc_only/fig2.png", plot = deg_scatter_plots, width = 10, height = 10)
print(cor.test(pcc_df$deg[pcc_df$deg<10&pcc_df$group=='real'],pcc_df$sens[pcc_df$deg<10&pcc_df$group=='real'],method='spearman',exact=FALSE))
```

# Figure2 C,D,E
```{r tags=c()}
pcc_rewire_df <- pcc_df_random%>%group_by(random_id)%>%
  summarise(
    eff_deg_pearson = cor.test(eff,deg)$estimate,
    sens_deg_spearman = cor.test(sens,deg, method="spearman",exact=FALSE)$estimate
  )
rewire_df <- pcc_rewire_df %>% mutate(data = "pcc")
network_labels <- c("Yeast GI Profile Similarity")
facet_labels <- network_labels
names(facet_labels) <- c("pcc")
combined_rewire_df <- rewire_df %>%
  select(data, eff_deg_pearson, sens_deg_spearman) %>%
  mutate(type = "random") %>%
  bind_rows(
    data.frame(
      sens_deg_spearman = c(cor(pcc_df[pcc_df$group == "real", ]$deg, pcc_df[pcc_df$group == "real", ]$sens, method = "spearman")),
      eff_deg_pearson = c(cor(pcc_df[pcc_df$group == "real", ]$deg, pcc_df[pcc_df$group == "real", ]$eff, method = "pearson")), type = "real", data = c("pcc")
    )
  ) %>%
  mutate(data = fct_relevel(data, c("pcc")))

p3 <-
  ggplot() +
  #    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
  #    geom_boxplot()+
  #    geom_jitter()+
  geom_density(data = combined_rewire_df %>% filter(type != "real"), aes(x = eff_deg_pearson, color = type, y = ..scaled..), linetype = "dashed") +
  geom_vline(data = combined_rewire_df %>% filter(type == "real"), aes(xintercept = eff_deg_pearson, color = type)) +
  guides(color = guide_legend(title = "Data type"), shape = guide_legend(title = "Network type")) +
  ylab("Density") +
  xlab("Effectiveness degree correlation") +
  theme_bw() +
  theme(panel.spacing = unit(2, "lines"),axis.text=element_text(size=text_size),axis.title = element_text(size=label_size)) +
  scale_y_continuous(expand = c(0, 0))
p4 <-
  ggplot() +
  #    facet_grid(cols = vars(data), labeller = labeller(data=facet_labels))+
  #    geom_boxplot()+
  #    geom_jitter()+
  geom_density(data = combined_rewire_df %>% filter(type != "real"), aes(x = sens_deg_spearman, y = ..scaled.., color = type), linetype = "dashed") +
  geom_vline(data = combined_rewire_df %>% filter(type == "real"), aes(xintercept = sens_deg_spearman, color = type)) +
  guides(color = guide_legend(title = "Data type"), shape = guide_legend(title = "Network type")) +
  ylab("Density") +
  xlab("Sensitivity degree correlation") +
  theme_bw() +
  theme(panel.spacing = unit(2, "lines"), legend.position = "bottom",axis.text=element_text(size=text_size),axis.title = element_text(size=label_size)) +
  scale_color_discrete(labels = c("Random networks", "Genetic network")) +
  scale_y_continuous(expand = c(0, 0))
lgn34 <- cowplot::get_legend(p4)

pcc_degree_dens <- cowplot::ggdraw(plot_density_prs(pcc_df, deg, xlab = "Degree") + theme(legend.position = "none",axis.text=element_text(size=text_size),axis.title = element_text(size=label_size))) #+
distr_plots <- plot_grid(pcc_degree_dens + theme(legend.position = ""),
  ggdraw(p3 + theme(legend.position = "")),
  ggdraw(p4 + theme(legend.position = "")),
  labels = c("C", "D", "E"), nrow = 1, rel_widths=c(0.3,0.35,0.35),label_size = 20
)
# distr_plots_withlgn <- plot_grid(distr_plots, lgn34,
# nrow=2,rel_heights = c(0.9,0.1))
# ggsave('reports/figures/paper_figures_0916/fig2.png',plot=distr_plots , width=7)
distr_plots
#plot_grid(deg_scatter_plots, distr_plots, pcc_dens_comb, nrow = 3, rel_heights = c(0.3, 0.4, .3))
#
#ggsave("reports/figures/paper_figures_0202_pcc_only/fig3.pdf", width = 10, height = 12)
```

# Figure2 G, F
```{r}
pcc_eff_dens <-
  plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness (a.u.)")
dens_lgn <- cowplot::get_legend(pcc_eff_dens + theme(legend.position = "right"))
#  cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
pcc_eff_dens <-
  cowplot::ggdraw(plot_density_prs(pcc_df, eff_norm, xlab = "Effectiveness (a.u.)") + theme(legend.position = "none",axis.text=element_text(size=text_size),axis.title = element_text(size=label_size)) +
    coord_trans(x = "log10", xlim = c(NA, 10e-2)) +
    scale_x_continuous(
      breaks = scales::trans_breaks("log10", function(x) 10^x),
      labels = scales::trans_format("log10", scales::math_format(10^.x))
    )) #+
#   cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
# annotate("text", x = 0.000001, y = 0.2, label=sprintf("p = %#.2f", eff_p), fontface='italic', size = 6)
pcc_sensitivity_dens <-
  cowplot::ggdraw(plot_density_prs(pcc_df, sens_norm, xlab = "Sensitivity (a.u.)") + theme(legend.position = "none",axis.text=element_text(size=text_size),axis.title = element_text(size=label_size))) #+
#        cowplot::draw_plot(dens_lgn, .55,.55,.5,.5)
# title <- cowplot::ggdraw() + cowplot::draw_label("Yeast GI Profile Similarity", fontface='bold')
pcc_dens_comb <- cowplot::plot_grid(pcc_eff_dens + theme(legend.position = "none"),
  pcc_sensitivity_dens + theme(legend.position = "none"),
  #+theme(legend.position='none'),
  labels = c("F", "G"), ncol = 2,label_size = 20
)
# pcc_dens_comb_title = cowplot::plot_grid(title, pcc_dens_comb, nrow=2 ,rel_heights=c(0.1,0.9))
# dens_lgn = cowplot::get_legend(pcc_sensitivity_dens)
#dens_plots <- 
  pcc_dens_comb

@@

```{r}
if(snakemake@params['save']==TRUE){
  figure_folder = "../reports/figures/paper_figures_052521/"
combined_plot <- plot_grid(deg_scatter_plots, distr_plots, pcc_dens_comb, nrow = 3, rel_heights = c(0.3, 0.2, .3))
ggsave(glue("{figure_folder}/fig2.png"),plot=combined_plot,width=12,height=12)
}
```

### 2021-11-16 notebooks/03-Fig3abde_4acd-051821.Rmd
updated supp figure notebooks

# Load packages
```{r message=FALSE, warning=FALSE}
#library(tidyverse)
if (!require('tidyverse')) {
   remotes::install_version("tidyverse", version = "1.3.0", repos = "http://cran.us.r-project.org")
   library(tidyverse)
}
if (!require('glue')) {
   remotes::install_version("glue", version = "1.4.1", repos = "http://cran.us.r-project.org")
   library(glue)
}
if (!require('cowplot')) {
   remotes::install_version("cowplot", version = "1.0.0", repos = "http://cran.us.r-project.org")
   library(cowplot)
}
if (!require('ggpubr')) {
   remotes::install_version('foreign',version="0.8-72", repos = "http://cran.us.r-project.org")
   remotes::install_version("ggpubr", version = "0.4.0", repos = "http://cran.us.r-project.org")
   library(ggpubr)
}
if (!require('ggsignif')) {
   remotes::install_version("ggsignif", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(ggsignif)
}
if (!require('RColorBrewer')) {
   remotes::install_version("RColorBrewer", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(RColorBrewer)
}
col <- brewer.pal(n = 9, name = "Set1")
sensor_colors <- brewer.pal(n = 12, name = "Set3")
effector_colors <- col[7:9] # brewer.pal(n=3, name= "Set1_r")
if(!require("FSA")){
  remotes::install_github('droglenc/FSA')
}
```

@@

@@

eff_deg_comp <- ggplot(effector_pcc %>% right_join(pcc_df)%>% 
                       mutate(go_group = factor(replace_na(as.character(go_group),"Others")),
                              go_group=fct_reorder(go_group, eff),
                              go_group= fct_relevel(go_group,'Others',after=Inf)), 
                       aes(x = go_group, y = deg, fill = go_group)) +
  geom_boxplot(outlier.shape = NA) +
   scale_fill_manual(
     values = c(effector_colors,'black'),
     labels = c("EC1 (Chromosome\nSegregation)", "EC2 (Golgi vesicle\nTransport)", "EC3 (Respiratory complex\nassembly)",'Non-effector genes')
   ) +
  xlab("") +
  ylab("Degree") +
  theme_bw() +
   geom_signif(
     comparisons = comparisons_effectors[order(sapply(comparisons_effectors, function(x) x[1], simplify=TRUE), decreasing=TRUE)], #list(c("golgi", "chromosome"), c("golgi", "mito"), c("mito", "chromosome")),
     annotation = c("*", "***", "ns"),
     y_position = c(115, 120, 130)
   ) +
  theme(
       axis.text.y=element_text(size=10),
        axis.title.y=element_text(size=14),legend.title = element_blank(),  axis.text.x = element_blank(), legend.text = element_text(margin = margin(t = 10, b = 10))) # , legend.spacing.y = unit(2,'in'))+
eff_deg_comp
```

@@

eff_eff_comp <- ggplot(effector_pcc %>% #mutate(go_group = fct_reorder(go_group, eff)) %>%
  mutate(eff_norm = eff / 5183), aes(x = go_group, y = eff_norm, fill = go_group)) +
  geom_boxplot() +
  xlab("") +
  ggpubr::stat_compare_means(method = "kruskal.test") +
   scale_fill_manual(values = effector_colors,
   labels = c("EC1 (Chromosome\nSegregation)", "EC2 (Golgi vesicle\nTransport)", "EC3 (Respiratory complex\nassembly)")) +
  ylab("Effectiveness (a.u.)") +
  theme_bw() +
  theme(
        axis.text.y=element_text(size=10),
        axis.title.y=element_text(size=14),axis.text.x = element_blank(), legend.title = element_blank())
eff_eff_comp
```

```{r}
if(snakemake@params['save']==TRUE){
  figure_folder = "../reports/figures/paper_figures_052521/"
ggsave(glue("{figure_folder}/fig3a.png"),plot=sensor_neighbor_degree_plot,width=3,height=3)
ggsave(glue("{figure_folder}/fig3b.png"),plot=sensor_connectivity_plot,width=3.5,height=2.5)
ggsave(glue("{figure_folder}/fig3d.png"),plot=sens_deg_comp+theme(legend.position='none'),width=3.9,height=2.1)
ggsave(glue("{figure_folder}/fig3e.png"),plot=sens_sens_comp+theme(legend.position='none'),width=3.9,height=2.1)

ggsave(glue("{figure_folder}/fig4a.png"),plot=eff_neighbor_degree_plot,width=3,height=3)
ggsave(glue("{figure_folder}/fig4c.png"),plot=eff_deg_comp+theme(legend.position='right'),width=3,height=3)
ggsave(glue("{figure_folder}/fig4d.png"),plot=eff_eff_comp+theme(legend.position='none'),width=3,height=3)

@@

        #guides(fill = guide_legend(override.aes = list(size = 5))))
legend_plot <- ggdraw(legend)
ggsave(glue("{figure_folder}/fig3d_legend.pdf"),plot=legend_plot, width=10, height=2)
}
```

>>>>

# Load packages
```{r message=FALSE, warning=FALSE, tags=c()}
#library(tidyverse)
if (!require('tidyverse')) {
   remotes::install_version("tidyverse", version = "1.3.0", repos = "http://cran.us.r-project.org")
   library(tidyverse)
}
if (!require('glue')) {
   remotes::install_version("glue", version = "1.4.1", repos = "http://cran.us.r-project.org")
   library(glue)
}
if (!require('cowplot')) {
   remotes::install_version("cowplot", version = "1.0.0", repos = "http://cran.us.r-project.org")
   library(cowplot)
}
if (!require('ggpubr')) {
   remotes::install_version('foreign',version="0.8-72", repos = "http://cran.us.r-project.org")
   remotes::install_version("ggpubr", version = "0.4.0", repos = "http://cran.us.r-project.org")
   library(ggpubr)
}
if (!require('ggsignif')) {
   remotes::install_version("ggsignif", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(ggsignif)
}
if (!require('RColorBrewer')) {
   remotes::install_version("RColorBrewer", version = "0.6.0", repos = "http://cran.us.r-project.org")
   library(RColorBrewer)
}
col <- brewer.pal(n = 9, name = "Set1")
sensor_colors <- brewer.pal(n = 12, name = "Set3")
effector_colors <- col[7:9] # brewer.pal(n=3, name= "Set1_r")
if(!require("FSA")){
  remotes::install_github('droglenc/FSA')
}
```

@@

```{r}
(1/10001)<0.0001
```

@@

eff_deg_comp <- ggplot(effector_pcc %>% right_join(pcc_df)%>% 
                       mutate(go_group = factor(replace_na(as.character(go_group),"Others")),
                              go_group=fct_reorder(go_group, eff),
                              go_group= fct_relevel(go_group,'Others',after=Inf)), 
                       aes(x = go_group, y = deg, fill = go_group)) +
  geom_boxplot(outlier.shape = NA) +
   scale_fill_manual(
     values = c(effector_colors,'black'),
     labels = c("EC1 (Chromosome\nSegregation)", "EC2 (Golgi vesicle\nTransport)", "EC3 (Respiratory complex\nassembly)",'Non-effector genes')
   ) +
    scale_x_discrete(labels=c('EC1','EC2','EC3','Non-effector\ngenes'))+
  xlab("") +
  ylab("Degree") +
  theme_bw() +
   geom_signif(
     comparisons = comparisons_effectors[order(sapply(comparisons_effectors, function(x) x[1], simplify=TRUE), decreasing=TRUE)], #list(c("golgi", "chromosome"), c("golgi", "mito"), c("mito", "chromosome")),
     annotation = c("*", "***", "ns"),
     y_position = c(115, 120, 130)
   ) +
  theme(
       axis.text.y=element_text(size=10),
        axis.title.y=element_text(size=14),legend.title = element_blank(), legend.text = element_text(margin = margin(t = 10, b = 10))) # , legend.spacing.y = unit(2,'in'))+
eff_deg_comp
```

@@

eff_eff_comp <- ggplot(effector_pcc %>% #mutate(go_group = fct_reorder(go_group, eff)) %>%
  mutate(eff_norm = eff / 5183), aes(x = go_group, y = eff_norm, fill = go_group)) +
  geom_boxplot() +
  xlab("") +
  ggpubr::stat_compare_means(method = "kruskal.test") +
   scale_fill_manual(values = effector_colors,
   labels = c("EC1 (Chromosome\nSegregation)", "EC2 (Golgi vesicle\nTransport)", "EC3 (Respiratory complex\nassembly)")) +
  ylab("Effectiveness (a.u.)") +
    scale_x_discrete(labels=c('EC1','EC2','EC3','Non-effector\ngenes'))+

  theme_bw() +
  theme(
        axis.text.y=element_text(size=10),
        axis.title.y=element_text(size=14), legend.title = element_blank())
eff_eff_comp
```

```{r}
#if(snakemake@params['save']==TRUE){
  figure_folder = "../reports/figures/paper_figures_052521/"
ggsave(glue("{figure_folder}/fig3a.png"),plot=sensor_neighbor_degree_plot,width=3,height=3)
ggsave(glue("{figure_folder}/fig3b.png"),plot=sensor_connectivity_plot,width=3.5,height=2.5)
ggsave(glue("{figure_folder}/fig3d.png"),plot=sens_deg_comp+theme(legend.position='none'),width=3.9,height=2.1)
ggsave(glue("{figure_folder}/fig3e.png"),plot=sens_sens_comp+theme(legend.position='none'),width=3.9,height=2.1)

ggsave(glue("{figure_folder}/fig4a.png"),plot=eff_neighbor_degree_plot,width=3,height=3)
ggsave(glue("{figure_folder}/fig4c.png"),plot=eff_deg_comp+theme(legend.position='none'),width=3,height=3)
ggsave(glue("{figure_folder}/fig4d.png"),plot=eff_eff_comp+theme(legend.position='none'),width=3,height=3)

@@

        #guides(fill = guide_legend(override.aes = list(size = 5))))
legend_plot <- ggdraw(legend)
ggsave(glue("{figure_folder}/fig3d_legend.pdf"),plot=legend_plot, width=10, height=2)
#}
```

```{r}
